---
title: "flat_study_squirrels.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---
# get_message_fur_color
    
```{r function-get_message_fur_color}
#' Get a message with the fur color of interest.
#' 
#' Get a message with the fur color of interest.
#' 
#' @param primary_fur_color Character. The primary fur color of interest
#' @importFrom glue glue
#' @return Nothing Used for side effect. Outputs a message in the console
#' 
#' @export
get_message_fur_color <- function(primary_fur_color){
  color_ok <- check_primary_color_is_ok(primary_fur_color)
  if(isTRUE(color_ok)){
     message(glue("We will focus on {primary_fur_color} squirrels"))
  }
  else{
    stop("Incorrect color provided")
  }
   
}
```
  
```{r example-get_message_fur_color , eval=FALSE}
get_message_fur_color(primary_fur_color = "Cinnamon")
```
  
```{r tests-get_message_fur_color}
test_that("get_message_fur_color works", {
  expect_message(
    object = get_message_fur_color(primary_fur_color = "Cinnamon"), 
    regexp = "We will focus on Cinnamon squirrels"
  )
  expect_error(
    object =get_message_fur_color(primary_fur_color = "sssddd"),
    regexp = "Incorrect color provided"
  )
  
  
  
  
})
```
  
<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)
library(glue)
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Include some data examples in your package

<!-- 
 Store your dataset in a directory named "inst/" at the root of your project.
 Use it for your tests in this Rmd thanks to `pkgload::load_all()` to make it available
and `system.file()` to read it in your examples.

- There already is a dataset in the "inst/" directory to be used in the examples below
-->

```{r development-dataset}
# Run all this chunk in the console directly
# There already is a dataset in the "inst/" directory
# Make the dataset file available to the current Rmd during development
pkgload::load_all(path = here::here(), export_all = FALSE)

# You will be able to read your example data file in each of your function examples and tests as follows - see chunks below
# datafile <- system.file("nyc_squirrels_sample.csv", package = "squirrels")
# nyc_squirrels <- read.csv(datafile, encoding = "UTF-8")
# 
# nyc_squirrels
```
# check_primary_color_is_ok
    
```{r function-check_primary_color_is_ok}
#' Check the values of primary fur color
#'
#' @param string Character. A vector with the primary fur color.
#'
#' @return Boolean. TRUE if all colors are correct.
#' @export
#'
#' @examples
check_primary_color_is_ok <- function(string) {
  all_colors_OK <- all(
    string %in% c("Gray", "Cinnamon", "Black", NA)
  )
  return(all_colors_OK)
}
```
  
```{r example-check_primary_color_is_ok , eval=FALSE}
check_primary_color_is_ok("Cinnamon")

```
  
```{r tests-check_primary_color_is_ok}
test_that("check_primary_color_is_ok works", {
  expect_true(inherits(check_primary_color_is_ok, "function")) 
  expect_true(object = check_primary_color_is_ok("Cinnamon"), TRUE)
  expect_false(object = check_primary_color_is_ok("dsdsds"), FALSE)

})
```
# Function to check squirrel data integrity

```{r}
#' Function to check squirrel data integrity
#' @param data_df Squirrel dataset
#' 
#' @return String returns a message with the data integrity information
#' 
#' @export 
#' 
#' @examples
check_squirrel_data_integrity <- function(data_df){
  
  if ("primary_fur_color" %in% names(data_df)){
    res <- check_primary_color_is_ok(data_df$primary_fur_color)
    if(isTRUE(res)){
      message("All primary colors are correct")
    }else{
      message("Not all primary colors correct")
    }
    
    
  }else{
    stop("primary_fur_color column not fount in the dataset")
  }
  
  
}


```
# Testing check_squirrel_data_integrity function

```{r test-check_squirrel_data_integrity}

test_that("check_squirrel_data_integrity works",
          {
            my_data <- readr::read_csv(
              file = system.file("nyc_squirrels_sample.csv",package="squirrels")
            )
            
            expect_message(check_squirrel_data_integrity(my_data),
                           regexp = "All primary colors are correct"
              
            )
            # Error: no primary_fur_color column in the dataset
            
          })



```



```{r}
data_path <- system.file("nyc_squirrels_sample.csv", package="squirrels")
sq_data_df <- readr::read_csv(data_path)
# names(sq_data_df)
# sq_data_df$primary_fur_color

check_squirrel_data_integrity(sq_data_df)
```


# Loading datasets

```{r}
usethis::use_data_raw()
```


```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_study_squirrels.Rmd", vignette_name = "Get started",overwrite = TRUE)
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
